Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-21 SecDev21/paper.tex
fixing typos
more Enlgish fixes

Although formal verification can only be applied to the SPARK translated code,  pre- and post-conditions can be attached to C functions interfaced in SPARK to allow reasoning about the side effects of calling these functions by the SPARK code. Since the functional specification of these contracts can not be proved, it is the role of the programmer to ensure their correctnes.

>>>>

Although formal verification can only be applied to the SPARK translated code,  pre- and post-conditions can be attached to C functions interfaced in SPARK to allow reasoning about the side effects of calling these functions by the SPARK code. Since the functional specification of these contracts can not be proved, it is the programmer's role to ensure their correctness. Interfacing C and SPARK code can be error-prone if it is not done carefully. \Cref{sec:verif} discusses how to mitigate this issue effectively.
